%----------------------------------------------------------------------------------------
%	DISCUSSION
%----------------------------------------------------------------------------------------
\section{Discussion}

TODO

\subsection{Comparison of classification approaches}

TODO: In this section, we can compare the different approaches we used to classify our data.


\subsubsection{Comparing architectures}

TODO: Comparing the architectures of the approaches.

\begin{itemize}
\item Are they comparable?
\item How is the structure different?
\item Which parameters are different?
\item Can we expect the results to be comparable?
\end{itemize}


\subsubsection{Comparing results}

TODO: Comparing the results of the different classification approaches.

\begin{itemize}
\item Which approach worked best?
\item Which values do we want to use for comparison? e.g.

\begin{itemize}
\item ROC curve (false positive (FP), true positive(TP)) 
\item validation accuracy
\item ...
\end{itemize}

\end{itemize}


\subsection{Final result of the project}

TODO: Our final conclusion on the project.


\subsubsection{Scientific results}

TODO: Short summary/evaluation of the project and its outcome on a scientific basis.

\begin{itemize}
\item What did we achieve in the end?
\item What went well and what did not work so well?
\item What would we do differently if we could start anew, what would we keep?
\item What problems did we run into and how did we solve them?
\item Were there any technical restrictions?
\end{itemize}


\subsubsection{Organization}

TODO: Short summary/evaluation of the project as a study project and teamwork experience.

\begin{itemize}
\item How did the organisation work?
\item What did we achieve in the end?
\item What went well and what did not work so well?
\item What would we do differently if we could start anew - what would we keep?
\item What problems did we run into and how did we solve them?
\end{itemize}

