%----------------------------------------------------------------------------------------
%	DATA ACQUISITION AND PREPARATIONS
%----------------------------------------------------------------------------------------
\section{Data acquisition and organization}

Organizing a working schedule for the year, collecting the data, and literature research.


\subsection{Timetable (roadmap) of the project}

A (visual) overview of the project's course during the year.

\begin{itemize}
\item how we planned the project
\item how the actual timetable of the project looked like
\end{itemize}


\subsection{Organisation of the study group}

Non-scientific part where we reflect on our working as a team and how we communicated.


\subsubsection{Communication}

Deciding on a communication platform and handling it.

\begin{itemize}
\item organization in general
\item team meetings
\item Asana, Telegram, and any other virtual form of communication
\end{itemize}


\subsubsection{Teamwork}

The experience of working in a team and organising/distributing tasks in a group.

\begin{itemize}
\item task distribution
\item cooperation on tasks
\item GitHub: organising our project with Git
\item Grid: working together with the IKW data store
\item other teamwork related experiences (could we integrate the strengths and weaknesses of the single team members)
\end{itemize}


\subsection{Data collection}

How we collected the data and what the data looked like. \\
Here, the process of driving to Rheine and collecting the data with an external hard-drive is described.

\begin{itemize}
\item Understanding the sorting machine and its output.
\item First problems that had to be resolved:

\begin{itemize}
\item labeled vs. unlabeled data ( -> running pre-sorted pieces through the sorting machine, did not (completely) resolve our problem)
\item saving the data manually on an external harddrive ( -> solved by building a script for data transfer, and Teamviewer sessions)
\end{itemize}

\end{itemize}


\subsection{Literature research}

Previous literature research concerning food classification and handling unlabeled data.

\begin{itemize}
\item Searching for background literature close to our project, e.g. automatic CV-based sorting of other food products.
\item Researching semi-supervised and unsupervised learning approaches.
\item Re-reading on potential ANN structures that we could use for sorting.
\item What was the result?
\item Could we rely on a certain paper/process? Did it work?
\end{itemize}


